Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-06 ms.tex
Finished first draft of abstract

\newcommand{\wprp}{w_{\mathrm{p}}}
\newcommand{\rp}{r_{\mathrm{p}}}

\bibliographystyle{mn2e}

@@

\maketitle
%----------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%  A B S T R A C T %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}

We fit SDSS DR7 data with models that include assembly bias.

Important points:
-supersedes previous analyses even for standard HOD.
-cannot rule out assembly bias using galaxy clustering.
-some samples favor assembly bias.

\end{abstract}

@@

Short summary of \citet{hearin_etal16}.

>>>>

\newcommand{\wprp}{w_{\mathrm{p}}}
\newcommand{\rp}{r_{\mathrm{p}}}
\newcommand{\magr}{M_r}
\bibliographystyle{mn2e}

@@

\maketitle
%----------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%  A B S T R A C T %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARZ: Important points:
% -supersedes previous analyses even for standard HOD.
% -cannot rule out assembly bias using galaxy clustering.
% -some samples favor assembly bias.
\begin{abstract}
We constrain the newly-introduced Decorated HOD model using SDSS DR7 measurements of projected galaxy clustering, $\wprp,$ and number density, $n_{\rm d},$ made from r-band luminosity-threshold samples. The Decorated HOD is a model for the galaxy--halo connection that augments the traditional Halo Occupation Distribution (HOD) by allowing for the possibility of {\em assembly bias}: galaxy luminosity may be correlated with dark matter halo properties besides virial mass $\mvir$ alone. We demonstrate that it is not possible to rule out assembly bias using DR7 measurements of $\wprp$ and $n_{\rm d}.$ Moreover, galaxy samples $\magr<-20, -20.5$ favor strong levels of central galaxy assembly bias: high-concentration halos are more likely to host a central galaxy relative to low-concentration halos of the same $\mvir.$ We rule out zero assembly bias with high significance for these samples. We find no evidence for assembly bias in the $\magr<-21$ sample, and only moderately significant levels of satellite assembly bias at any luminosity. Because the Decorated HOD subsumes the traditional HOD, and additionally because of errors made in the original analysis of these samples, our results differ from and supersede existing HOD constraints from low-redshift clustering measurements. 
\end{abstract}

@@

In addition to the standard occupation statistics described in the previous section, in this paper we also use the decorated HOD formalism to connect galaxies to dark matter halos in a manner that has simultaneous dependence on both $\mvir$ and halo concentration. Briefly, we use Equations \ref{eq:ncen} and \ref{eq:nsat} as our ``baseline" first occupation moments. At fixed $\mvir,$ halos are divided into one of two categories, those of high- and low-concentration, depending on whether the concentration of the halo places it above or below the rank-order percentile $f_{\rm split},$ which we keep fixed to $f_{\rm split}=0.5$ throughout the paper. High-concentration halos have a different first occupation moment relative to low-concentration halos of the same mass, $\langle\ngal|\mvir, c_{\rm high}\rangle \neq \langle\ngal|\mvir, c_{\rm low}\rangle.$ The difference between the first moment of high- and low-concentration halos is modulated by $\abias,$ the novel parameter of the decorated HOD governing assembly bias. Values of $\abias=\pm1$ correspond to the maximum strength of assembly bias allowable by the constraint that the model preserves the marginalized first moment, $\langle\ngal|\mvir\rangle;$ thus regardless of the value of $\abias,$ in the decorated HOD the marginalized first moment of centrals and satellites are unchanged from the baseline value defined by Equations \ref{eq:ncen} and \ref{eq:nsat}. We refer the reader to \citet{hearin_etal16} for further details about the decorated HOD.
